Inferring Graphics Programs from Images

### 2017-05-14 synthesizerOutputs.tex
updated extrapolation results

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-41.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Rectangle(0,0,1,6)
  Rectangle(2,0,3,6)
  Rectangle(4,0,5,6)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-17.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Rectangle(2,9,4,11)
    for (3)
        Line(-2*i + 7,3*i + 3,-2*i + 6,3*i + 1,arrow = True,solid = True)
        Line(2*i + 3,-3*i + 9,2*i + 4,-3*i + 7,arrow = True,solid = True)
        Rectangle(2*i,-3*i + 6,2*i + 2,-3*i + 8)
        Rectangle(-2*i + 8,3*i,-2*i + 10,3*i + 2)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-43.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
      Line(0,0,0,5,arrow = False,solid = True)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-63.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Rectangle(0,0,5,5)
  Rectangle(1,1,4,4)
  Rectangle(2,2,3,3)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-11.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Circle(1,1)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-45.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Rectangle(0,4,4,8)
        reflect(y = 12)
        Circle(7,6)
        Line(2,2,2,4,arrow = True,solid = True)
        Line(4,6,6,6,arrow = True,solid = True)
        Rectangle(1,0,3,2)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-51.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Rectangle(2,2,5,3)
  Rectangle(0,0,3,1)
  Rectangle(4,4,7,5)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-21.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Circle(1,5)
    for (2)
        Line(-5*i + 9,-1*i + 2,-7*i + 9,-3*i + 4,arrow = True,solid = True)
        Rectangle(-4*i + 8,4*i,-4*i + 10,4*i + 2)
              reflect(x = 6)
              Line(7*i + 1,-1*i + 2,5*i + 1,-3*i + 4,arrow = True,solid = True)
              Rectangle(8*i,4*i,8*i + 2,4*i + 2)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-2.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Rectangle(4,2,6,5)
        reflect(y = 7)
        Line(2,6,4,4,arrow = True,solid = True)
        Rectangle(0,5,2,7)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-24.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Line(3,3,3,2,arrow = True,solid = True)
  Rectangle(0,7,6,9)
  Rectangle(2,0,4,2)
  Rectangle(0,3,6,6)
        Line(1,7,1,6,arrow = True,solid = True)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-7.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  for (3)
      Circle(-3*i + 7,1)
      Circle(3*i + 1,6)
      Line(3*i + 1,2,3*i + 1,5,arrow = False,solid = True)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-44.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
      reflect(x = 12)
      Circle(4,1)
      Line(9,1,10,1,arrow = False,solid = True)
      Rectangle(10,0,12,2)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-64.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
      reflect(x = 6)
      Line(5,2,5,4,arrow = False,solid = True)
            reflect(y = 6)
            Line(2,5,4,5,arrow = False,solid = True)
            Rectangle(0,4,2,6)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-36.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  for (2)
      Rectangle(0,-3*i + 8,1,-2*i + 9)
      Rectangle(-3*i + 8,5*i,9,8*i + 1)
      Rectangle(-7*i + 7,-2*i + 2,-5*i + 9,4)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-58.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Rectangle(4,0,5,4)
    for (2)
        Line(8,0,-8*i + 8,-7*i + 7,arrow = True,solid = True)
        Rectangle(-4*i + 6,0,-4*i + 7,-2*i + 5)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-3.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Circle(10,5)
  Line(7,5,9,5,arrow = True,solid = True)
  Rectangle(5,3,7,7)
  Rectangle(0,0,12,10)
        reflect(y = 10)
        Line(3,2,5,4,arrow = True,solid = True)
        Rectangle(1,1,3,3)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-28.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Line(0,0,0,2,arrow = False,solid = True)
  Line(0,2,2,2,arrow = False,solid = True)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-22.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Line(8,5,6,5,arrow = True,solid = True)
  Line(4,5,2,5,arrow = True,solid = True)
    for (3)
        Line(-4*i + 9,4,-4*i + 9,2,arrow = True,solid = True)
        Rectangle(4*i,0,4*i + 2,2)
        Rectangle(-4*i + 8,4,-4*i + 10,6)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-69.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Rectangle(0,4,5,6)
        reflect(x = 5)
        Circle(4,1)
        Line(1,4,1,2,arrow = True,solid = True)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-14.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Rectangle(0,6,1,7)
    for (3)
        Rectangle(-2*i + 6,2*i,-2*i + 7,2*i + 1)
        Rectangle(-2*i + 4,2*i,-2*i + 5,2*i + 1)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-68.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  for (3)
      Circle(4*i + 1,1)
      Rectangle(4*i,0,4*i + 2,2)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-65.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
      reflect(y = 6)
      Line(2,1,4,1,arrow = False,solid = True)
            reflect(x = 6)
            Circle(1,1)
            Line(1,2,1,4,arrow = False,solid = True)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-67.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Line(1,5,5,1,arrow = False,solid = True)
  Line(1,4,5,0,arrow = False,solid = True)
  Rectangle(5,0,6,1)
  Rectangle(0,4,1,5)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-12.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  for (2)
      Circle(-5*i + 6,1)
      Line(-4*i + 6,-1*i + 2,-1*i + 6,-4*i + 5,arrow = False,solid = True)
      Line(-1*i + 2,-4*i + 6,-4*i + 5,-1*i + 6,arrow = False,solid = True)
      Rectangle(5*i,5,5*i + 2,7)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-42.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Line(0,0,0,5,arrow = False,solid = False)
  Line(4,1,4,5,arrow = False,solid = False)
  Line(4,0,4,1,arrow = False,solid = False)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-10.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Rectangle(0,0,3,4)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-35.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Circle(1,1)
    for (2)
        Circle(-5*i + 6,5*i + 1)
        Line(1,5,5*i + 1,2,arrow = True,solid = True)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-31.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Circle(7,3)
    for (3)
        Circle(-3*i + 7,5)
        Circle(-3*i + 7,2*i + 1)
        Rectangle(-3*i + 6,2*i,-3*i + 8,6)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-37.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Circle(1,8)
    for (2)
        Line(4*i + 1,-5*i + 7,2*i + 3,5,arrow = False,solid = True)
        Rectangle(-4*i + 4,5*i,6,7*i + 2)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-40.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Circle(7,1)
  Circle(4,1)
  Circle(1,1)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-29.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Line(1,2,1,5,arrow = False,solid = True)
    for (2)
        Line(2,-4*i + 4,-4*i + 6,4,arrow = False,solid = True)
        Line(0,-2*i + 6,-2*i + 2,6,arrow = False,solid = True)
        Line(1,5,2*i + 2,5,arrow = False,solid = True)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-62.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Rectangle(5,0,8,3)
  Rectangle(2,1,4,3)
  Rectangle(0,2,1,3)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-57.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  for (3)
      Circle(-4*i + 9,4)
      Circle(-4*i + 9,1)
      Circle(4*i + 1,7)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-55.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Circle(1,5)
  Line(1,4,1,2,arrow = True,solid = True)
  Rectangle(0,0,2,2)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-66.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Line(0,2,7,2,arrow = False,solid = True)
  Line(1,1,6,1,arrow = False,solid = True)
  Line(2,0,5,0,arrow = False,solid = True)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-26.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Circle(1,9)
  Line(1,8,1,6,arrow = True,solid = True)
  Line(1,3,1,2,arrow = True,solid = True)
  Line(1,3,1,4,arrow = False,solid = True)
        reflect(y = 6)
        Circle(1,1)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-15.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Line(1,2,3,2,arrow = False,solid = True)
  Line(2,1,4,1,arrow = False,solid = False)
  Line(3,0,5,0,arrow = False,solid = True)
  Line(0,3,2,3,arrow = False,solid = False)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-19.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Line(4,4,2,2,arrow = True,solid = True)
  Rectangle(3,4,5,6)
  Rectangle(0,0,2,2)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-8.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Line(0,0,0,4,arrow = False,solid = True)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-23.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Line(4,1,2,1,arrow = False,solid = True)
    for (2)
        Line(-4*i + 5,2,-4*i + 5,4,arrow = True,solid = True)
          for (3)
              Circle(-4*j + 9,4*i + 1)
              Line(8,1,3*i + 6,3*i + 1,arrow = True,solid = False)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

>>>>

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-0.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
  line(6,2,6,3,arrow = False,solid = True)
  line(6,2,3,2,arrow = True,solid = True)
  rectangle(0,0,8,9)
  rectangle(5,3,7,6)
        reflect(y = 9)
        line(3,7,5,5,arrow = True,solid = True)
        rectangle(1,6,3,8)
        \end{verbatim}
\end{minipage}

    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-2.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
  rectangle(4,2,6,5)
        reflect(y = 7)
        line(2,6,4,4,arrow = True,solid = True)
        rectangle(0,5,2,7)
        \end{verbatim}
\end{minipage}

    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-3.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
  circle(10,5)
  line(3,2,5,4,arrow = True,solid = True)
    for (2)
        line(-4*i + 7,3*i + 5,-4*i + 9,5,arrow = True,solid = True)
        rectangle(-5*i + 5,-3*i + 3,5*i + 7,3*i + 7)
        rectangle(1,6*i + 1,3,6*i + 3)
        \end{verbatim}
\end{minipage}

    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-4.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
  circle(10,4)
  line(10,1,10,3,arrow = False,solid = False)
  line(10,1,2,1,arrow = True,solid = False)
  rectangle(4,2,7,6)
        reflect(y = 8)
        line(2,1,4,3,arrow = True,solid = True)
        line(7,4,9,4,arrow = True,solid = True)
        rectangle(0,0,2,2)
        \end{verbatim}
\end{minipage}

    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-5.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
  line(12,9,12,0,arrow = True,solid = True)
    for (2)
        rectangle(3*i + 6,-2*i + 5,3*i + 8,9)
        rectangle(3*i,7,3*i + 2,9)
        \end{verbatim}
\end{minipage}

    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-6.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
  line(0,4,3,4,arrow = False,solid = True)
  rectangle(2,0,5,3)
    for (2)
        line(3*i,3*i + 1,3*i + 2,3*i,arrow = False,solid = True)
        line(0,-3*i + 4,-2*i + 2,3,arrow = False,solid = True)
        \end{verbatim}
\end{minipage}

    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-7.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
  for (3)
      circle(3*i + 1,6)
      circle(-3*i + 7,1)
      line(-3*i + 7,-1*i + 4,-3*i + 7,5,arrow = False,solid = True)
        \end{verbatim}
\end{minipage}

    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-8.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
  line(0,0,0,4,arrow = False,solid = True)
        \end{verbatim}
\end{minipage}

    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-9.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
  line(6,0,0,0,arrow = True,solid = True)
        \end{verbatim}
\end{minipage}

    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-10.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
  rectangle(0,0,3,4)
        \end{verbatim}
\end{minipage}

    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-11.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
  circle(1,1)
        \end{verbatim}
\end{minipage}

    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-12.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
  for (2)
      circle(-5*i + 6,1)
      line(2,5*i + 1,5,5*i + 1,arrow = False,solid = True)
      line(5*i + 1,2,5*i + 1,5,arrow = False,solid = True)
      rectangle(-5*i + 5,5,-5*i + 7,7)
        \end{verbatim}
\end{minipage}

    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-13.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
  line(2,1,4,1,arrow = True,solid = True)
  line(5,0,3,0,arrow = True,solid = True)
  line(0,3,2,3,arrow = True,solid = True)
  line(3,2,1,2,arrow = True,solid = True)
        \end{verbatim}
\end{minipage}

    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-14.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
  rectangle(6,0,7,1)
    for (3)
        rectangle(-2*i + 4,2*i + 2,-2*i + 5,2*i + 3)
        rectangle(-2*i + 4,2*i,-2*i + 5,2*i + 1)
        \end{verbatim}
\end{minipage}

    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-15.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
  line(3,0,5,0,arrow = False,solid = True)
  line(2,1,4,1,arrow = False,solid = False)
  line(0,3,2,3,arrow = False,solid = False)
  line(1,2,3,2,arrow = False,solid = True)
        \end{verbatim}
\end{minipage}

    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-16.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
  circle(9,1)
    for (3)
        circle(2*i + 3,-3*i + 10)
        circle(2*i + 1,-3*i + 7)
        line(-2*i + 6,3*i + 1,-2*i + 7,3*i + 3,arrow = False,solid = True)
        line(-2*i + 7,3*i + 3,-2*i + 8,3*i + 1,arrow = False,solid = True)
        \end{verbatim}
\end{minipage}

    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-17.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
  rectangle(8,0,10,2)
    for (3)
        line(-2*i + 7,3*i + 3,-2*i + 8,3*i + 1,arrow = True,solid = True)
        line(2*i + 3,-3*i + 9,2*i + 2,-3*i + 7,arrow = True,solid = True)
        rectangle(-2*i + 6,3*i + 3,-2*i + 8,3*i + 5)
        rectangle(-2*i + 4,3*i,-2*i + 6,3*i + 2)
        \end{verbatim}
\end{minipage}

    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-18.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
  for (2)
      circle(-1*i + 4,-2*i + 5)
      circle(-6*i + 7,3*i + 3)
      circle(-2*i + 7,1)
        \end{verbatim}
\end{minipage}

    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-19.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
  line(4,4,2,2,arrow = True,solid = True)
  rectangle(3,4,5,6)
  rectangle(0,0,2,2)
        \end{verbatim}
\end{minipage}

    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-20.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
  rectangle(0,4,2,6)
    for (2)
        circle(4*i + 5,4*i + 1)
        line(4*i + 4,5,4*i + 2,5,arrow = True,solid = True)
              reflect(x = 10)
              circle(4*i + 5,-4*i + 5)
              line(4*i + 5,4,4*i + 5,2,arrow = True,solid = True)
        \end{verbatim}
\end{minipage}

    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-21.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
  circle(1,5)
    for (2)
        line(-4*i + 8,1,-4*i + 6,1,arrow = True,solid = True)
        rectangle(4*i + 4,4*i,4*i + 6,4*i + 2)
              reflect(x = 10)
              line(-4*i + 5,2,-4*i + 5,4,arrow = True,solid = True)
              rectangle(4*i,4*i,4*i + 2,4*i + 2)
        \end{verbatim}
\end{minipage}

    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-22.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
  line(4,5,2,5,arrow = True,solid = True)
  line(8,5,6,5,arrow = True,solid = True)
    for (3)
        line(4*i + 1,4,4*i + 1,2,arrow = True,solid = True)
        rectangle(4*i,0,4*i + 2,2)
        rectangle(-4*i + 8,4,-4*i + 10,6)
        \end{verbatim}
\end{minipage}

    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-23.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
  for (2)
      line(-4*i + 8,1,-4*i + 6,1,arrow = True,solid = True)
            reflect(x = 10)
            circle(5,-4*i + 5)
            circle(-8*i + 9,4*i + 1)
            line(-4*i + 9,2,-4*i + 9,4,arrow = True,solid = True)
        \end{verbatim}
\end{minipage}

    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-24.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
  line(5,7,5,6,arrow = True,solid = True)
  rectangle(2,0,4,2)
    for (2)
        line(2*i + 1,-4*i + 7,2*i + 1,-4*i + 6,arrow = True,solid = True)
        rectangle(0,4*i + 3,6,3*i + 6)
        \end{verbatim}
\end{minipage}

    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-25.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
  line(3,1,2,1,arrow = True,solid = True)
  rectangle(6,0,8,2)
        reflect(x = 5)
        line(6,1,5,1,arrow = True,solid = True)
        rectangle(3,0,5,2)
        \end{verbatim}
\end{minipage}

    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-26.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
  line(1,3,1,4,arrow = False,solid = True)
  line(1,3,1,2,arrow = True,solid = True)
  line(1,8,1,6,arrow = True,solid = True)
    for (3)
        circle(1,4*i + 1)
        \end{verbatim}
\end{minipage}

    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-27.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
      line(0,1,1,0,arrow = False,solid = True)
      line(1,2,2,1,arrow = False,solid = True)
        \end{verbatim}
\end{minipage}

    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-28.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
  line(0,2,2,2,arrow = False,solid = True)
  line(0,0,0,2,arrow = False,solid = True)
        \end{verbatim}
\end{minipage}

    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-29.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
  for (3)
      line(0,-1*i + 6,2*i + 2,-1*i + 6,arrow = False,solid = True)
      line(-1*i + 2,2*i,-1*i + 2,4,arrow = False,solid = True)
        \end{verbatim}
\end{minipage}

    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-30.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
  rectangle(0,0,2,2)
    for (2)
        circle(1,-3*i + 4)
        circle(5,-2*i + 4)
        rectangle(-4*i + 4,2*i + 1,-4*i + 6,5)
        \end{verbatim}
\end{minipage}

    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-31.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
  circle(4,3)
    for (3)
        circle(-3*i + 7,5)
        circle(7,-2*i + 5)
        rectangle(-3*i + 6,2*i,-3*i + 8,6)
        \end{verbatim}
\end{minipage}

    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-32.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
  circle(5,5)
  line(2,5,4,5,arrow = False,solid = True)
  rectangle(0,4,2,6)
  rectangle(0,0,5,3)
        \end{verbatim}
\end{minipage}

    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-33.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
  line(0,3,6,3,arrow = False,solid = False)
  line(0,0,0,3,arrow = False,solid = True)
  line(0,0,6,0,arrow = False,solid = False)
  line(6,0,6,3,arrow = False,solid = True)
        \end{verbatim}
\end{minipage}

    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-34.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
  for (2)
      line(-1*i + 2,-1*i + 3,-1*i + 2,-1*i + 5,arrow = False,solid = True)
      line(3,-3*i + 3,5,-3*i + 3,arrow = False,solid = True)
      line(4*i,-5*i + 5,2*i + 2,-3*i + 5,arrow = False,solid = True)
      line(-4*i + 5,1,-2*i + 5,-1*i + 3,arrow = False,solid = True)
        \end{verbatim}
\end{minipage}

    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-35.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
  circle(1,6)
    for (2)
        circle(-5*i + 6,1)
        line(-1*i + 2,-1*i + 6,-5*i + 6,2,arrow = True,solid = True)
        \end{verbatim}
\end{minipage}

    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-36.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
  for (2)
      rectangle(-8*i + 8,5*i,-7*i + 9,6*i + 1)
      rectangle(0,-8*i + 8,3*i + 1,-5*i + 9)
      rectangle(-2*i + 7,3*i + 2,9,5*i + 4)
        \end{verbatim}
\end{minipage}

    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-37.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
  circle(1,8)
    for (2)
        line(-4*i + 5,5*i + 2,-2*i + 5,5,arrow = False,solid = True)
        rectangle(4*i,-5*i + 5,6,-7*i + 9)
        \end{verbatim}
\end{minipage}

    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-40.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
  circle(4,1)
        reflect(x = 8)
        circle(1,1)
        \end{verbatim}
\end{minipage}

    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-41.png}&

        \begin{minipage}{10cm}
        \begin{verbatim}
  rectangle(0,0,1,6)
  rectangle(4,0,5,6)
  rectangle(2,0,3,6)
        \end{verbatim}
\end{minipage}

    \end{tabular}        
            \\

            \begin{tabular}{ll}
    \includegraphics[width = 5cm]{../TikZ/drawings/expert-42.png}&
